Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-28 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add some to text

The most often used hurricane exposure criteria at the county-level include FEMA disaster declarations [GBA-- are these that commonly used? We should certainly put them in as one way to measure exposure, but I don't know if we want to include them, with distance, as "most often used" unless we can find quite a few examples of them being used to determine exposure] and whether a county's perimeter intercepts a swath describing a buffer a certain distance from the storm's central track. These ways of assessing exposure can be nonspecific and potentially lead to misclassification of exposure at the county-level [@Grabich2016]. FEMA declaration is largely subjective, requiring state governors and/or tribal chiefs to submit a proposal for government aid on the basis that local resources are overwhelmed [@FEMA]. As a result, using FEMA disaster declarations as exposure classification to hurricanes restricts exposure to 1) those states whose resources are overwhelmed and 2) those states who apply for FEMA aid. As a result, other severely impacted counties and states that may not fit FEMA criteria are excluded and may therefore be incorrectly identified as unexposed, preventing researchers from assessing the full impact of a given hurricane [JMF-- the Grabich 2016 study actually found that FEMA assigned the highest exposure, and may overestimate the health effects of a hurricane; GBA-- let's think about why that might have had "false positives". I think that would be an interesting point to include here.]. Researchers have found heterogeneity in exposure assignments of counties, both within and between storms, when different metrics of exposure are used [@Grabich2016; @Grabich2015]. Such missclassification can have important consequences in assessments of the public health and economic impacts of tropical storms.

>>>>

Good Characteristics:
- Flooding-- Most associated with death; property damage
- Precipitation
- Wind (potentially weighted)

Bad Characteristics:
- Distance alone
- Wind alone

Hurricane exposure criteria at the county-level include FEMA disaster declarations [GBA-- are these that commonly used? We should certainly put them in as one way to measure exposure, but I don't know if we want to include them, with distance, as "most often used" unless we can find quite a few examples of them being used to determine exposure], whether a county's perimeter intercepts a swath describing a buffer a certain distance from the storm's central track, or exposure metrics based primarily on sustained wind speeds (i.e., the Staffir-Simpson scale). These ways of assessing exposure can be nonspecific and potentially lead to misclassification of exposure at the county-level [@Grabich2016; @Fronstin1994]. FEMA declaration is largely subjective, requiring state governors and/or tribal chiefs to submit a proposal for government aid on the basis that local resources are overwhelmed [@FEMA]. As a result, using FEMA disaster declarations as exposure classification to hurricanes restricts exposure to 1) those states whose resources are overwhelmed and 2) those states who apply for FEMA aid. As a result, other severely impacted counties and states that may not fit FEMA criteria are excluded and may therefore be incorrectly identified as unexposed, preventing researchers from assessing the full impact of a given hurricane [JMF-- the Grabich 2016 study actually found that FEMA assigned the highest exposure, and may overestimate the health effects of a hurricane; GBA-- let's think about why that might have had "false positives". I think that would be an interesting point to include here.]. Researchers have found heterogeneity in exposure assignments of counties, both within and between storms, when different metrics of exposure are used [@Grabich2016; @Grabich2015]. Such missclassification can have important consequences in assessments of the public health and economic impacts of tropical storms.
